---
title: "Analyses of Tabitha's May 2017 Microbiome invasion experiments"
author: "Douglas Yu"
date: "02 May 2017"
output: html_document
---

**  interesting point to consider for analysis.  One of the Strepto strains (coelicolorM1146) has had its antibiotic production clusters (4 of them) deleted and thus might grow intrinsically faster.  need to check. 

Main results:  
1. Analysis with lme4: *removal of most of the correlation amongst residuals by using 3 random intercepts* (Ps.strain, Inv.strain, Plate).
2. Significant Invader:mediainfusion interaction: *Streptomyces grows relatively more quickly in Ps-infused media*
3. Significant Ps.genotype main effect (using a subset of the data that includes Ps1 and Ps2 only):  *Ps2 suppresses growth more effectively*

To do:
4. Calculate effect sizes of Invader:mediainfusion interaction, Ps.genotype main effect
5. fix beeswarm command on line 107.
6. still some correlated residuals in Plate random effect
7. get data that lets me convert Inv.strain and Ps.strain random effects to main effects.

## Housekeeping
```{r, message=FALSE}
# rm(list=ls())
library(nlme)
library(readxl)
library(dplyr)
library(stringr)
library(knitr)
library(lattice)
library(forcats)
library(beeswarm)
library(lme4)
library(sjPlot)
library(openxlsx)
# tidyverse_packages()
```

```{r}
datafile <- "Block 2 Ps bioassays_data tables_20170502_20170516.xlsx"
```

A test sentence.

## Assay 1:  Can _Streptomyces_ invade an antibiotic-laden environment (_Pseudonocardia_)?
```{r}
assay1 <- read_excel(datafile, sheet = "data_table_Strep", na = "NA")
tbl_df(assay1) # should have 530 rows and 1 cols
assay1 <- assay1 %>% select(-Input.order, -Plate.orig, -Notes, -Standardised.score, -Spore.production)
assay1$Ps.strain <- as.factor(assay1$Ps.strain)
assay1$Ps.genotype <- as.factor(assay1$Ps.genotype)
assay1$Invader <- as.factor(assay1$Invader)
assay1$Inv.strain <- as.factor(assay1$Inv.strain)
assay1$Plate <- as.factor(assay1$Plate)
assay1 <- assay1 %>% filter(!str_detect(Invasion.score, 'discount|discount plate')) # one way to filter by string rather than numeric value
assay1$Invasion.score <- as.numeric(assay1$Invasion.score)
assay1 # should have 492 rows and 6 cols
```

```{r}
assay1noctrl <- assay1 %>% filter(!str_detect(Ps.genotype, 'Control'))
# assay1noctrl <- assay1 %>% filter(Ps.genotype %in% c("Ps1", "Ps2", "unknown")) # alternative
assay1noctrl$Ps.genotype <- droplevels(assay1noctrl$Ps.genotype)
```

Mean Streptomyces invasion zone = `r round(summarise(assay1noctrl, mean(Invasion.score)), 2)` ± `r round(summarise(assay1noctrl, sd(Invasion.score)/sqrt(length(assay1noctrl$Invasion.score))), 2)` SE mm

```{r}
(wilcox.test(assay1noctrl$Invasion.score, mu=0))
```


## Assay 2:  Can _Non-antibiotic-producers_ invade an antibiotic-laden environment (_Pseudonocardia_)?

```{r, warning=FALSE}
assay2 <- read_excel(datafile, sheet = "data_table_Sb", na = "NA")
tbl_df(assay2) # should have 520 rows and 10 cols
assay2 <- assay2 %>% select(-Input.order, -Plate.orig, -Notes, -Standardised.score, -Spore.production)
assay2$Ps.strain <- as.factor(assay2$Ps.strain)
assay2$Ps.genotype <- as.factor(assay2$Ps.genotype)
assay2$Invader <- as.factor(assay2$Invader)
assay2$Inv.strain <- assay2$Inv.strain + 10 # to differentiate numbering from Strepto samples
assay2$Inv.strain <- as.factor(assay2$Inv.strain)
# assay2$Plate <- assay2$Plate + 10 # to differentiate numbering from Strepto samples
assay2$Plate <- as.factor(assay2$Plate)
assay2 <- assay2 %>% filter(!str_detect(Invasion.score, 'discount|discount plate'))
assay2$Invasion.score <- as.numeric(assay2$Invasion.score)
assay2 # should have 483 rows and 6 cols
```

```{r}
assay2noctrl <- assay2 %>% filter(!str_detect(Ps.genotype, 'Control'))
assay2noctrl$Ps.genotype <- droplevels(assay2noctrl$Ps.genotype)
```

Mean invasion zone = `r round(summarise(assay2noctrl, mean(Invasion.score)), 2)` ± `r round(summarise(assay2noctrl, sd(Invasion.score)/sqrt(length(assay2noctrl$Invasion.score))),2)` SE mm

```{r}
(wilcox.test(assay2noctrl$Invasion.score, mu=0))
```


## Assay 3:  Is _Streptomyces_ better than _Soft bugs_ at invading an antibiotic-laden environment (_Pseudonocardia_)?  
```{r assay3, message=FALSE, warning=FALSE}
assay3 <- bind_rows(assay1, assay2)
assay3$Invader <- as.factor(assay3$Invader)
assay3$Inv.strain <- factor(assay3$Inv.strain)
assay3$Plate <- as.factor(assay3$Plate)
assay3$Ps.strain <- relevel(assay3$Ps.strain, "Control")
tbl_df(assay3)
xtabs(~ Inv.strain + Ps.strain, assay3)
```

```{r boxplot of results}
boxplot(Invasion.score~Invader:Ps.genotype, ylab=expression("Mean colony area " ~ (cm^{2})), cex.axis=.7, cex.lab=0.8, outline=FALSE, ylim=c(0.0,1.8), whisklty=0, staplelty=0, boxlty=1, boxwex=0.3, data=assay3)

# beeswarm(Invasion.score~Invader:Ps.genotype, vertical=TRUE, pch=16, method="swarm", cex=.6, col=as.numeric(assay3$Ps.strain), add=TRUE, data=assay3)

stripchart(Invasion.score~Invader:Ps.genotype, vertical=TRUE, pch=16, method="jitter", jitter=.03, cex=.3, add=TRUE, data=assay3)
```

These are used to choose strains for the competition experiment
```{r assay4 summary data tables, eval=FALSE}
(assay4.1 <- assay3 %>% group_by(Ps.genotype, Invader) %>% summarise(median.Invasion.score=round(median(Invasion.score), 2)))

assay4.2 <- assay3 %>% group_by(Ps.genotype, Invader, Inv.strain) %>% summarise(median.Invasion.score=round(median(Invasion.score), 2))
assay4.2 <- assay4.2 %>% arrange(Ps.genotype, Invader, median.Invasion.score)
assay4.3 <- assay3 %>% group_by(Ps.genotype, Ps.strain, Invader, Inv.strain) %>% summarise(median.Invasion.score=round(median(Invasion.score), 2))

write.table(assay4.1, file = "assay4.1.tsv", quote = FALSE, sep = "\t") # use this to choose summary pairs for the competition experiment
write.table(assay4.2, file = "assay4.2.tsv", quote = FALSE, sep = "\t") # use this to choose summary pairs for the competition experiment
write.table(assay4.3, file = "assay4.3.tsv", quote = FALSE, sep = "\t") # use this to choose summary pairs for the competition experiment

# openxlsx::write.xlsx(assay4.2, file = "assay4.2_test.xlsx", colNames = TRUE)
```

To read the boxplot:
The y-axis is the area (cm^2^) of the invading colony's growth. 
1. On control media (left 2 columns), Soft-bug colonies are bigger than Streptomyces colonies (i.e. Streptomyces grow more slowly). 
2. However, on Pseudonocardia media (Ps1, Ps2, unknown genotypes), Soft-bug colonies are smaller. (i.e. Streptomyces colonies grow more quickly).
3. Growth is generally higher on Ps1 media than on Ps2 + unknown media (i.e. Ps2 and unknown are more effective overall inhibitors).
4. I guess that the unknown Ps genotype is Ps2.

# Results 1 and 2 above are an interaction between Invader and mediainfusion. 

```{r}
# make a column that collapses the three Pseudonocardia genotypes into "Ps"
assay3$mediainfusion <- fct_collapse(assay3$Ps.genotype, PS = c("Ps1", "Ps2", "unknown"), ctrl = c("Control"))

boxplot(Invasion.score~Invader:mediainfusion, ylab=expression("Mean colony area " ~ (cm^{2})), cex.axis=.7, cex.lab=0.8, outline=FALSE, ylim=c(0.0,1.8), whisklty=0, staplelty=0, boxlty=1, boxwex=0.3, data=assay3)
stripchart(Invasion.score~Invader:mediainfusion, vertical=TRUE, pch=16, method="jitter", jitter=.02, cex=.3, add=TRUE, data=assay3)

assay5 <- assay3 %>% group_by(Ps.strain, mediainfusion, Invader, Inv.strain) %>% summarise(mean.Invasion.score=mean(Invasion.score))

mod1 <- lm(mean.Invasion.score~Invader*mediainfusion, data=assay5)
mod2 <- update(mod1, ~. - Invader:mediainfusion)
anova(mod1, mod2)
summary(mod1)
par(mfrow=c(2, 2))
plot(mod2)
par(mfrow=c(1, 1))
```

Final model is:  mean.Invasion.score ~ Invader * mediainfusion
Soft bugs grow faster in the Ps-free control media, and Streptomyces grow faster in the Ps-infused media. (p=0.0254)
This is not a very good model, due to heteroscedasticity and non-normal residuals. 

Also, there are correlated residuals due to 3 random factors:
```{r}
levels(assay3$Ps.strain)
levels(assay3$Inv.strain)
levels(assay3$Plate)
```

1. Pseudonocardia strain: `Ps.strain` (17 levels: A, B, D, E, F, G, J, K, L, M, N, Ø, P, Q, R, S, T) 
2. Invader strain: `Inv.strain` (20 levels: 1-20) 
3. Petri-dish: `Plate` (20 levels: 1-20) 

The experiment is fully crossed but slightly unbalanced, so that every Inv.strain is tested against every Ps.strain (usually 30 times = 3 plates, sometimes 20 times = 2 plates). 

There are 2 fixed factors:  
1. Pseuonocardia genotype: `Ps.genotype` (Control, Ps1, Ps2, unknown). Unknown is probably Ps2, given the response values. Control is no Pseudonocardia
2. Pseudonocardia:  `mediainfusion` (ctrl, PS).  
3. Invader type: `Invader`(Soft_bugs (non-producers), Streptomyces)

Finally, the response variable is:
1. Mean colony area (cm^2^): `Invasion.score`

I test for an interaction effect between `Invader` and `mediainfusion` to see if Streptomyces and Soft bugs reverse their superiorities when moving from control to Ps-infused media.

####

```{r, eval=FALSE}
# with(assay3, dotchart(Invasion.score, groups = Ps.strain, color = as.numeric(Invader), ylab="Ps.strain", xlab="Invasion.score", main="black=Soft bugs, red=Streptomyces"))

# print(dotplot(reorder(Inv.strain, Invasion.score) ~ Invasion.score, assay3, groups = Plate, ylab = "Inv.strain", xlab = expression("Mean colony area " ~ (cm^{2})), main = "Plates", type = c("p", "a"), auto.key = list(columns = 3, lines = TRUE)))

print(dotplot(reorder(Ps.strain, Invasion.score) ~ Invasion.score, assay3, groups = Inv.strain, ylab = "Ps.strain", xlab = expression("Mean colony area " ~ (cm^{2})), main = "Inv.strain", type = c("p", "a"), auto.key = list(columns = 3, lines = TRUE))) 

# with(assay3, dotchart(Invasion.score, groups = Inv.strain, color = as.numeric(Ps.genotype), main="red/green=Ps2, black=Ps1"))
```

Dotchart shows that Streptomyces growth is relatively greater on Ps-infused media, is relatively lower on Control media, and some Ps.strains cause overall low growth. 

Dotplot shows that Inv.strain 18 has highest overall growth (dark green line to the right side).  There is also an Inv.strain 81, 16, or 4, can't tell), which grows very poorly (line on left hand side). A large part of the overall variance is caused by differences amongst Inv.strain.

```{r Check for correlated residuals}
M1 <- lm(Invasion.score~Invader*Ps.genotype, data=assay3)
E1 <- rstandard(M1)
par(mfrow=c(2, 2))
plot(E1 ~ assay3$Ps.strain); abline(0,0) # P,Q,T strains mostly below 0, so possibly a Ps.strain effect
plot(E1 ~ assay3$Inv.strain); abline(0,0) # many strains mostly above or below 0, so possibly an Inv.strain effect
plot(E1 ~ assay3$Plate); abline(0,0) # multiple plates mostly above or below 0, so possibly a plate effect (note: there are 99 plates)
par(mfrow=c(1, 1))
rm(M1)
rm(E1)
```

Ps.strain, Inv.strain, and Plate all appear to have correlated residuals, esp. Inv.strain and Plate


######
# lme4 version of analysis (dataset = assay3)
Testing if there is a significant effect of Ps-infused media on the winning invader

```{r}
# random intercepts only
M1 <- lmer(Invasion.score ~ Invader*mediainfusion + (1|Ps.strain) + (1|Inv.strain) + (1|Plate), data=assay3, REML = FALSE)

M2 <- lmer(Invasion.score ~ Invader + mediainfusion + (1|Ps.strain) + (1|Inv.strain) + (1|Plate), data=assay3, REML = FALSE)

anova(M1, M2) # highly significant, p=0.00114
AIC(M1, M2) # M1 has lower AIC 220.8375
coef(M1)
fixef(M1)
summary(M1)
# sjp.resid(M1) # no idea what this is for, and it also wastes cycles
sjp.lmer(M1, type = "re.qq", y.offset = 0.4)
sjp.lmer(M1, y.offset = 0.4)

qqmath(ranef(M1))
```

Using only random intercepts, the best model is M1 (AIC=220.8): 

Invasion.score ~ Invader * Ps.genotype + (1 | Ps.strain) + (1 | Inv.strain) + (1 | Plate)

Random and Fixed factors:
```{r}
par(mfrow=c(2, 2))
plot(assay3$Ps.strain, resid(M1), xlab="Ps.strain", ylab="Residuals"); abline(0,0)
plot(assay3$Inv.strain, resid(M1), xlab="Inv.strain", ylab="Residuals"); abline(0,0)
plot(assay3$Plate, resid(M1), xlab="Plate", ylab="Residuals"); abline(0,0)
par(mfrow=c(1,1))

plot(assay3$Ps.genotype, resid(M1), xlab="Ps.genotype", ylab="Residuals"); abline(0,0)
plot(assay3$Invader, resid(M1), xlab="Invader", ylab="Residuals"); abline(0,0)
```

The residuals of the random factors show almost no structure (except for Plates, which still has some correlated residuals). Soft bugs show greater residual variance than do Streptomyces. 

Now i estimate coefficients

```{r}
# to estimate coefficients, set REML=TRUE
M1.1 <- lmer(Invasion.score ~ Invader*mediainfusion + (1|Ps.strain) + (1|Inv.strain) + (1|Plate), data=assay3, REML = TRUE)

# coef(M1.1)
summary(M1.1)
fixef(M1.1) # Streptomyces grow relatively faster on Ps-infused media
# sjp.resid(M1.1)
sjp.lmer(M1.1, type = "re.qq", y.offset = 0.4)
sjp.lmer(M1.1, y.offset = 0.4)
qqmath(ranef(M1.1))
```

Inv.strain is the biggest contributor of variance, followed by Residual variance. There is 7X less variance caused by Plate (albeit this part is unbalanced), and 8X less variance caused by Ps.strain.

Random effects:
 Groups     Name        Variance Std.Dev.
 Plate      (Intercept) 0.01458  0.1207  
 Inv.strain (Intercept) 0.10528  0.3245  
 Ps.strain  (Intercept) 0.01268  0.1126  
 Residual               0.05685  0.2384  
Number of obs: 975, groups:  Plate, 99; Inv.strain, 20; Ps.strain, 18

Random and Fixed factors:
```{r}
par(mfrow=c(2, 2))
plot(assay3$Ps.strain, resid(M1.1), xlab="Ps.strain", ylab="Residuals"); abline(0,0)
plot(assay3$Inv.strain, resid(M1.1), xlab="Inv.strain", ylab="Residuals"); abline(0,0)
plot(assay3$Plate, resid(M1.1), xlab="Plate", ylab="Residuals"); abline(0,0)
# still some correlated residuals with Plate, which need to be removed somehow, perhaps with Plate as a random slope?
par(mfrow=c(1, 1))


plot(assay3$Ps.genotype, resid(M1.1), xlab="Ps.genotype", ylab="Residuals"); abline(0,0)
plot(assay3$Invader, resid(M1.1), xlab="Invader", ylab="Residuals"); abline(0,0)
```

# Now test for the effect Ps1 vs. Ps2. Delete the "Control" and "unknown" levels in Ps.genotype. 

```{r}
assay6 <- assay3 %>% filter(Ps.genotype %in% c("Ps1", "Ps2"))
assay6$Ps.genotype <- droplevels(assay6$Ps.genotype)

M7 <- lmer(Invasion.score ~ Invader*Ps.genotype + (1|Ps.strain) + (1|Inv.strain) + (1|Plate), data=assay6, REML = FALSE)

M8 <- lmer(Invasion.score ~ Invader + Ps.genotype + (1|Ps.strain) + (1|Inv.strain) + (1|Plate), data=assay6, REML = FALSE)

M9  <- lmer(Invasion.score ~ Invader + (1|Ps.strain) + (1|Inv.strain) + (1 |Plate), data=assay6, REML = FALSE)

anova(M7, M8) # no sig interaction effect p=0.1537
anova(M8, M9) # sig effect of Ps.genotype, p=0.004239, best model M8 AIC = 159.82

# Estimate parameters with REML = TRUE
M8.1 <- lmer(Invasion.score ~ Invader + Ps.genotype + (1|Ps.strain) + (1|Inv.strain) + (1|Plate), data=assay6, REML = TRUE)

summary(M8.1)
fixef(M8.1) # Ps2 causes a lower growth rate (-0.179)
# sjp.resid(M8.1)
sjp.lmer(M8.1, type = "re.qq", y.offset = 0.4)
sjp.lmer(M8.1, y.offset = 0.4)
qqmath(ranef(M8.1))
```

Fixed effects:
                    Estimate Std. Error t value
(Intercept)          0.81323    0.10760   7.558
InvaderStreptomyces  0.03164    0.14043   0.225
Ps.genotypePs2      -0.17937    0.05676  -3.160


Random and Fixed factors:
```{r}
par(mfrow=c(2, 2))
plot(assay6$Ps.strain, resid(M8.1), xlab="Ps.strain", ylab="Residuals"); abline(0,0)
plot(assay6$Inv.strain, resid(M8.1), xlab="Inv.strain", ylab="Residuals"); abline(0,0)
plot(assay6$Plate, resid(M8.1), xlab="Plate", ylab="Residuals"); abline(0,0)
par(mfrow=c(1, 1))

plot(assay6$Ps.genotype, resid(M8.1), xlab="Ps.genotype", ylab="Residuals"); abline(0,0)
plot(assay6$Invader, resid(M8.1), xlab="Invader", ylab="Residuals"); abline(0,0)
```




######
# nlme mixed-effect model (dataset = assay3)
The full model with no random factors is:

```{r, eval=FALSE, include=FALSE}
M1 <- gls(Invasion.score ~ Invader*Ps.genotype, data=assay3)
summary(M1) # aliased to Ps.genotype = control. 
M1.1 <- gls(Invasion.score ~ Invader*mediainfusion, data=assay3)
summary(M1.1) # aliased to media = control
```

Either way, there is a significant interaction effect, such that Streptomyces do better on Ps-infused media

The full model with random factors is:

```{r, eval=FALSE, include=FALSE}
M2 <- lme(Invasion.score~Invader*Ps.genotype, random = ~1 | Inv.strain, data=assay3)
M2.1 <- lme(Invasion.score~Invader*Ps.genotype, random = ~1 | Ps.strain, data=assay3)

anova(M1,M1.1,M2)
anova(M1,M1.1,M2,M2.1)
```

`r 0.5 * (1 - pchisq(362.5, 1))` # p is basically 0

M2 has a much lower AIC value (379.0) than M1 (1074.9), M1.1 (1082.7), and M2.1 (1061.5), which isn't too surprising, since we saw autocorrelated residuals.

```{r, eval=FALSE, include=FALSE}
plot(M1, col=as.numeric(assay3$Ps.genotype))
plot(M1.1, col=as.numeric(assay3$mediainfusion))
plot(M2, col=as.numeric(assay3$Ps.genotype))
plot(M2, col=as.numeric(assay3$Invader)) 
```

Random and Fixed factors:
```{r, eval=FALSE, include=FALSE}
plot(assay3$Ps.strain, resid(M2), xlab="Ps.strain", ylab="Residuals"); abline(0,0)
plot(assay3$Inv.strain, resid(M2), xlab="Inv.strain", ylab="Residuals"); abline(0,0)
plot(assay3$Plate, resid(M2), xlab="Plate", ylab="Residuals"); abline(0,0)

plot(assay3$Invader, resid(M2), xlab="Invader", ylab="Residuals"); abline(0,0)
plot(assay3$Ps.genotype, resid(M2), xlab="Ps.genotype", ylab="Residuals"); abline(0,0)
plot(assay3$mediainfusion, resid(M2), xlab="mediainfusion", ylab="Residuals"); abline(0,0)
```

Ps.strain and Plate have heterogeneous residuals (less so Inv.strain).

Invader, Ps.genotype, and medinfusion have heterogeneous residuals.  In particular, Softbugs have larger residuals than do Streptomyces, which is probably because they have a wider range of genotypes (different genera).

Trying to remove heteroscedasticity.
```{r, eval=FALSE, include=FALSE}
M3 <- lme(Invasion.score~Invader*Ps.genotype, random = ~ 1 | Inv.strain, weights = varIdent(form = ~ 1 | Invader), data=assay3)

anova(M2, M3)
E3 <- resid(M3, type="normalized")
boxplot(E3 ~ Invader, ylab="Normalized residuals", vertical=T, data=assay3)
```

M3 has a lower AIC (288.0) but still has heterogeneous residuals (less so than in M2, however). 

```{r, eval=FALSE, include=FALSE}
M4 <- lme(Invasion.score~Invader*Ps.genotype, random = ~ 1 | Inv.strain, weights = varIdent(form = ~ 1 | Invader*Ps.genotype), data=assay3)

anova(M2, M3, M4)
E4 <- resid(M4, type="normalized")
boxplot(E4 ~ Invader, ylab="Normalized residuals", vertical=T, data=assay3)
densityplot(~E4,data=assay3,groups = Invader, plot.points = FALSE, ref = TRUE, auto.key = list(space = "right"))
plot(assay3$Invader, resid(M4), xlab="Invader", ylab="Residuals"); abline(0,0)
plot(assay3$Ps.genotype, resid(M4), xlab="Ps.genotype", ylab="Residuals"); abline(0,0)
plot(assay3$mediainfusion, resid(M4), xlab="mediainfusion", ylab="Residuals"); abline(0,0)

```

M4 has an even lower AIC (281.2), but there is still a lot of heteroscedasticity. I'm done here for now. 
I can't add `Inv.strain` or `Ps.strain` to the weights function (model doesn't converge). So I'm done.


```{r, eval=FALSE, include=FALSE}
M4full <- lme(Invasion.score~Invader*Ps.genotype, random = ~ 1 | Inv.strain, weights = varIdent(form = ~ 1 | Invader*Ps.genotype), method = "ML", data=assay3)

M4sub <- update(M4full, ~.-Invader*Ps.genotype)

anova(M4full, M4sub)
```

Removal of the interaction term results in a significant difference (p<0.0001), and M4full has a lower AIC value (246.3) compared to M4sub (AIC = 325.1), so we keep the full model.

```{r, eval=FALSE, include=FALSE}
Mfinal <- lme(Invasion.score~Invader*Ps.genotype, random = ~ 1 | Inv.strain, weights = varIdent(form = ~ 1 | Invader*Ps.genotype), method = "REML", data=assay3)

qqnorm(Mfinal)
intervals(Mfinal, which="fixed")
summary(Mfinal)
```

However, I suspect that Ps.genotype 'unknown' is really Ps2. So let's combine "Ps2" and "unknown" into Ps2.

```{r Combining Ps.genotypes, eval=FALSE, include=FALSE}
assay3$Ps.genotype.comb <- fct_collapse(assay3$Ps.genotype, Ps2 = c("Ps2", "unknown", "unknown"), Ps1 = c("Ps1"), Control = c("Control"))

assay3$Ps.genotype.comb <- as.factor(assay3$Ps.genotype.comb)

M4full2 <- lme(Invasion.score~Invader*Ps.genotype.comb, random = ~ 1 | Inv.strain, weights = varIdent(form = ~ 1 | Invader*Ps.genotype.comb), method = "ML", data=assay3)

M4sub2 <- update(M4full, ~.-Invader*Ps.genotype.comb)

anova(M4full2, M4sub2)
anova(M4full, M4full2)
summary(M4full2)
```

There is a significant difference between M4full2 and Mfsub2 (p<0.0001), so it is still worth keeping the interaction term. Streptomyces grows relatively faster on Ps1/2 media. 

However, the AIC value for M4full2 is higher (258.5) than M4full, so it's worth using M4full and not combining "unknown" into "Ps2".


```{r, eval=FALSE, include=FALSE}
purl("Invasion analyses_20170502.Rmd")
```

